TBD

### 2020-11-01 outputs/paper/paper.Rmd
author and thanks

---
title: "TBD"
subtitle: "TBD"
author: "TBD"
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | First sentence. Second sentence. Third sentence. Fourth sentence. 
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r}
fit <- stan_glmer(#try using glmer()
  binary ~ factor(male) + factor(male) * factor(age) +
    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
  family = binomial(link = "logit"),
  data = clean_survey#all age, state etc coming from post-strat
)
```

```{r}
# to get the estimated proportions and associated 95% PIs by state
res_state <- fit %>%
  add_predicted_draws(newdata=state_prop %>% 
                        filter(age_group>20, age_group<80, decade_married>1969),
                      allow_new_levels=TRUE) %>%
  rename(kept_name_predict = .prediction) %>% 
  mutate(kept_name_predict_prop = kept_name_predict*prop) %>% 
  group_by(state_name, .draw) %>% 
  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
  group_by(state_name) %>% 
  summarise(mean = mean(kept_name_predict), 
            lower = quantile(kept_name_predict, 0.025), 
            upper = quantile(kept_name_predict, 0.975))
```

```{r}
# graph by state
res_state %>% 
  arrange(-mean) %>% 
  left_join(d %>%
              group_by(state_name, kept_name) %>%
              summarise(n = n()) %>%
              group_by(state_name) %>%
              mutate(prop = n/sum(n)) %>%
              filter(kept_name==1)) %>% 
  ggplot(aes(y = mean, x = forcats::fct_inorder(state_name), color = "MRP estimate")) + 
  geom_point() +
  coord_flip() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) + 
  ylab("proportion keeping maiden name") + 
  xlab("state") + 
  geom_point(aes(state_name, prop, color = "raw data")) +
  scale_color_manual(name = "", values = c("MRP estimate" = "black", "raw data" = "red")) + 
  theme_bw() +
  ggtitle("Proportion of women keeping maiden name after marriage")

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Arjun Dhatt, Benjamin Draskovic, Yiqu Ding, Gantavya Gupta"
thanks: "Code and data are available at: https://github.com/STA304-PS4/Trump-vs-Biden."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: |
  | First sentence. Second sentence. Third sentence. Fourth sentence. 
output:
  bookdown::pdf_document2:
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

@@

```{r, eval=FALSE}
fit <- stan_glmer(#try using glmer()
  binary ~ factor(male) + factor(male) * factor(age) +
    (1 | state) + (1 | age) + (1 | eth) + (1 | income),
  family = binomial(link = "logit"),
  data = clean_survey#all age, state etc coming from post-strat
)
```

```{r, eval=FALSE}
# to get the estimated proportions and associated 95% PIs by state
res_state <- fit %>%
  add_predicted_draws(newdata=state_prop %>% 
                        filter(age_group>20, age_group<80, decade_married>1969),
                      allow_new_levels=TRUE) %>%
  rename(kept_name_predict = .prediction) %>% 
  mutate(kept_name_predict_prop = kept_name_predict*prop) %>% 
  group_by(state_name, .draw) %>% 
  summarise(kept_name_predict = sum(kept_name_predict_prop)) %>% 
  group_by(state_name) %>% 
  summarise(mean = mean(kept_name_predict), 
            lower = quantile(kept_name_predict, 0.025), 
            upper = quantile(kept_name_predict, 0.975))
```

```{r, eval=FALSE}
# graph by state
res_state %>% 
  arrange(-mean) %>% 
  left_join(d %>%
              group_by(state_name, kept_name) %>%
              summarise(n = n()) %>%
              group_by(state_name) %>%
              mutate(prop = n/sum(n)) %>%
              filter(kept_name==1)) %>% 
  ggplot(aes(y = mean, x = forcats::fct_inorder(state_name), color = "MRP estimate")) + 
  geom_point() +
  coord_flip() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) + 
  ylab("proportion keeping maiden name") + 
  xlab("state") + 
  geom_point(aes(state_name, prop, color = "raw data")) +
  scale_color_manual(name = "", values = c("MRP estimate" = "black", "raw data" = "red")) + 
  theme_bw() +
  ggtitle("Proportion of women keeping maiden name after marriage")
